Synthesizing Quotient Lenses

### 2017-11-13 papers/QuotientLenses/main.tex
change quotientlensssynth folder to quotientlenses folder

As far as synthesis goes, though there is a good deal of recent research on
synthesizing unidirectional string
transformations~\cite{singh2012learning,le-pldi-2014,gulwani-popl-2014,
perelman2014test,Singh:blinkfill}, our system Optician, which we introduced in
~\cite{popl18}, is the first attempt to synthesize bidirectional
transformations that we are aware of. We compared Optician to two of these
unidirectional string transformers, Flash Fill~\cite{gulwani-popl-2014} and
FlashExtract~\cite{le-pldi-2014}, and found that these tools were unsuccessful
in synthesizing the complex transformations that can be expressed in Optician.
Furthermore, neither of these tools were able to infer transformations 
that occurred under two iterations.

Much of the research in synthesis assumes that the synthesizer is provided with
a collection of examples. Optician differs in that it requires that the
programmer supplies both examples {\em and} format descriptions in the form of
regular expressions. There are many other recent results showing how to
synthesize functions from type-based
specifications~\cite{augustsson-2004,osera+:pldi15,
feser-pldi-2015,scherer-icfp-2015,frankle+:popl16,armando+:pldi16}.
These systems enumerate programs of their target language, orienting their
search procedures to process only terms that are well-typed.
Optician is distinctive in that it synthesizes terms in a language with many
type equivalences. 
Perhaps the system most similar to Optician is InSynth~\cite{gvero-pldi-2013}, a
system for synthesizing terms in the simply-typed lambda calculus that addresses
equivalences on types.

>>>>

As far as synthesis goes, though there is a good deal of recent research on
synthesizing unidirectional string
transformations~\cite{singh2012learning,le-pldi-2014,gulwani-popl-2014,perelman2014test,Singh:blinkfill}, our system Optician, which we introduced in
~\cite{popl18}, is the first attempt to synthesize bidirectional
transformations that we are aware of. We compared Optician to two of these
unidirectional string transformers, Flash Fill~\cite{gulwani-popl-2014} and
FlashExtract~\cite{le-pldi-2014}, and found that these tools were unsuccessful
in synthesizing the complex transformations that can be expressed in Optician.
Furthermore, neither of these tools were able to infer transformations 
that occurred under two iterations.

Much of the research in synthesis assumes that the synthesizer is provided with
a collection of examples. Optician differs in that it requires that the
programmer supplies both examples {\em and} format descriptions in the form of
regular expressions. There are many other recent results showing how to
synthesize functions from type-based
specifications~\cite{augustsson-2004,osera+:pldi15,feser-pldi-2015,scherer-icfp-2015,frankle+:popl16,armando+:pldi16}.
These systems enumerate programs of their target language, orienting their
search procedures to process only terms that are well-typed.
Optician is distinctive in that it synthesizes terms in a language with many
type equivalences. 
Perhaps the system most similar to Optician is InSynth~\cite{gvero-pldi-2013}, a
system for synthesizing terms in the simply-typed lambda calculus that addresses
equivalences on types.
